Machine learning assignment  

Executive summary 
=================
This report is  about predicting human activities, say a forearm curl. We intend to build a model to predict which session could be classified as good and labeled A or not then B,C,D,or E, in the variable classe with five levels (A,B,C,D,E).
We have abuilt a support vector machine, and then assess the model accuracy while tuning cross parameter.
---
downloading data
``` 
training.csv = download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv",
                        destfile = "D:/R/Data/Machine learning/training.csv")
testing.csv = download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv",
                            destfile = "D:/R/Data/Machine learning/testing.csv")
```
```{r}
train = read.csv("D:/R/Data/Machine learning/training.csv")
test = read.csv("D:/R/Data/Machine learning/testing.csv")
acc_var = grep("^acc",names(train))
gyro_var = grep("^gyros",names(train))
train= train[,c(acc_var,gyro_var,160)]
test =  test[,c(acc_var,gyro_var,160)]
rm(acc_var,gyro_var)
```
Including library

```{r, echo = TRUE, warning = FALSE, message = FALSE}

library(e1071)
```
features selection  :  
------------------    
Here we have selected acceleration and gyration because these features 
quantify kinematics of a given motion. 

``` {r, echo = FALSE}

train = read.csv("D:/R/Data/Machine learning/training.csv")
test = read.csv("D:/R/Data/Machine learning/testing.csv")
Var = grep("^acc|^gyro",names(train))
train = train[,c(Var,160)]
test = test[,c(Var,160)]
```
Building model :      
-------------   
We have built our, from the default settings. Then we tune it step by step. we've first fixed gamma and used a sequence of k-folds ranging from 1 to to 10. There was a slice improvement in the total accuracy. However, when holding, k fixed to 5 and varying gamma, from default to .1, total accuracy improved from 83 % to 93 .4 %. However, one may prefer to use tune function or best.tune over svm model object to achieve this purpose.  

```{r}
set.seed (1)
svm.fit = svm(classe~.,data = train,gamma = .1,cross = 5)
summary(svm.fit)
table(predict(svm.fit,test))
```
 Conclusion :  
============        
Our model, has a total accuracy of 93.4 % and predicted 80% of the 20 cases in test data set.

